---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---


```{r setup}

library(batchanalytics)
library(bupaR)
#library(bamalog)
library(tidyr) # warum brauche ich das noch für gather aber die anderen package(bama) nicht mehr da imported mit package batchAanalytics---


```

Load sample eventlog 


```{r}

csv = system.file("exdata", "sample_data_1.csv", package = "batchanalytics")

csv_log = read.csv(csv)

task_log <- csv_log


```


detect batching behaviour and create a task log

add documentation why seq_list

```{r}


result_log <- my_detect_batching(task_log)



```

```{r}
#code refacor df_list
#1 ersetzen

#df_lists <- get_batching_df_logs(result_log)

get_batching_df_logs(result_log)


```







###batch processing metrics

```{r}
# transformation to event_logs
#2 unterer code ersetzten

transform_df_to_event_log()

```







##show process model with batching behaviour

```{r}

# create this as new method -> aber auch daran denken das "no batching" eine option ist 


class(show_batching_in_process_map())



#identfy which activites are performed with batching behaviour and if possible highlight in output graph or give an additional text output

```





## Cycle Time

The throughput time is the time form the very first event to the last event of a case. The levels at which it can be computed are log, trace, or case.

(overall cycle time, see pic bupR waiting time included)


```{r}


#evtl nicht nögig


#cycle time function without bupaR


#view github implementation of bupaR 
# compare to niels function implementation

#result_log %>% group_by("case_id") %>% 


```



```{r}

# create this as new method -> aber auch daran denken das "no batching" eine option ist 




#when writing method consider that not always all batch types are included and also no batching possible -> when plotting and creating boxplot create a generic approach#


# für modularität keep event log cration seperate from other functions 

#evtl cycle time selber funktion ohne event log schreiben -> von jeden case start - endzeit (groubby case , start - end , -> mean() an niels orientieren) ähnlich für processing time -< vorher #ABER data spliten in "nobatching " vs andere batch types


compare_throughput_time()



```




##processing time
processing time: the sum of the duration of all activity instances[bupaR]


```{r}



# create this as new method -> aber auch daran denken das "no batching" eine option ist 
# modularer aufbau der funktionen


compare_processing_time() # warum global env und nicht function


```


#idle time
idle time: the time when no activity instance is active



```{r}


compare_idle_time()

 


```


#Metric cycle time efficiency
Ratio of overall processing time relative to the overall cycle time


```{r}
#cycle time efficiency


# create this as new method -> aber auch daran denken das "no batching" eine option ist 
# modularer aufbau der funktionen



# processing time / throughput time


cycle_time_efficiency()



```



##metric batch frequency

This metrics shows .....

```{r}
#test batch frequency



metric_frequency(result_log, "B", "WorkerB_#0", "concurrent", FALSE )
```



```{r}

#test batch size
#metric_frequency(result_log, "Registration", "r1", "concurrent", FALSE )

metric_batch_size(result_log, "B", "WorkerB_#0", "concurrent", exclude_singletons = TRUE)

```



```{r}
# Metric - Activity duration
metric_activity_duration(result_log, "B", "WorkerB_#0", "concurrent")



```
```{r}

#create event log for bupaR

  #result_log %>% eventlog( case_id = "case_id", activity_id = "activity")


```



